\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-28 paper.tex
fixed unresolved reference

Although the finished product works as intended, we encountered several issues
along the way. The changing scope and goal of the project meant we spent several
weeks researching and working on features that did not make it into the final
product (see Section~\ref{sec:pivots}), such as displaying images in 3D AR space
and playing spatialized audio. If we had focused only on the features that made
it into the final app from the start we could have had more time to polish and
refine those features.

>>>>

Although the finished product works as intended, we encountered several issues
along the way. The changing scope and goal of the project meant we spent
several weeks researching and working on features that did not make it into the
final product (see Section~\ref{sec:alternativeArAppConcepts}), such as
displaying images in 3D AR space and playing spatialized audio. If we had
focused only on the features that made it into the final app from the start we
could have had more time to polish and refine those features.
